---
title: "2_DINEOF_IN_R"
author: "Digvijay Ghotane"
date: "11/9/2020"
output: html_document
---
This file imputes missing data for each variable. Please note that this is computationally VERY expensive (may take a very long time to run). It took me about 3-4 hours to run this chunk of code. Please return to the Jupyter notebook after you run this.

#Libraries
```{r}
require(tidyverse)
#require(devtools)
#devtools::install_github("marchtaylor/sinkr")
require(sinkr)
```

# Reading the QoG3 csv file that was exported from the .ipynb file - 1_analysis.ipynb
```{r}
data = read_csv('data/qog3_apply_dineof.csv') %>% select(-X1)
```

# Applying DINEOF algorithm to the dataframe by first converting it into a matrix
```{r}
data_dineof = dineof(unname(as.matrix(data)))
```

```{r}
cols = names(data) # Getting column names to reassign to new imputed matrix
new_data_frame_imputed = as.data.frame(data_dineof$Xa) # Storing new imputed matrix as df
names(new_data_frame_imputed) = cols # Assigning column names
```

# Writing back to csv to load into the .ipynb file - 1_analysis.ipynb
```{r}
new_data_frame_imputed %>% write_csv("data/imputed_data.csv")
```

